InteroceptionScale (study 2) - Data Analysis

### 2025-02-04 study2/analysis/2_analysis.qmd
Big changes
1) update items based on latest discussions
2) change keys of items to match dimensions on the table.html
3) added labels to the new items (analysis.qmd)

TODO
1. updated pre-processing

```{r}
labels <- list(
  MINT_Deficit_CaCo_4 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
  MINT_Deficit_CaCo_5 =  "I often feel like I can't get enough oxygen by breathing normally"
)
# TODO
```

>>>>

-   items commneted out - need to decide if keep or not

```{r}
labels <- list(
  MINT_Deficit_Urin_1 = "I sometimes feel like I need to urinate or defecate but when I go to the bathroom I produce less than I expected",
  MINT_Deficit_Urin_2 = "I often feel the need to urinate even when my bladder is not full",
  MINT_Deficit_Urin_3 = "Sometimes I am not sure whether I need to go to the toilet or not (to urinate or defecate)",
  MINT_Deficit_CaCo_4 = "Sometimes my breathing becomes erratic or shallow and I often don't know why",
  MINT_Deficit_CaCo_5 = "I often feel like I can't get enough oxygen by breathing normally",
  MINT_Deficit_CaCo_6 = "Sometimes my heart starts racing and I often don't know why",
  MINT_Deficit_CaNo_7 = "I often only notice how I am breathing when it becomes loud",
  MINT_Deficit_CaNo_8 = "I only notice my heart when it is thumping in my chest",
  MINT_Deficit_CaNo_9 = "I often only notice how I am breathing when my breathing becomes shallow or irregular",
  MINT_Deficit_Olfa_10 = "I often check the smell of my armpits",
  MINT_Deficit_Olfa_11 = "I often check the smell of my own breath",
  MINT_Deficit_Olfa_12 = "I often check the smell of my farts",
  #MINT_Deficit_Sati_13 = "I don't always feel the need to eat until I am really hungry",
  #MINT_Deficit_Sati_14 = "Sometimes I don't realise I was hungry until I ate something",
  #MINT_Deficit_Sati_15 = "I don't always feel the need to drink until I am really thirsty",
  # MINT_Awareness_SexA_16 = "I always feel in my body if I am sexually aroused",
  # MINT_Awareness_SexA_17 = "I can always tell that I am sexually aroused from the way I feel inside",
  # MINT_Awareness_SexA_18 = "I always know when I am sexually aroused",
  MINT_Awareness_SexS_19 = "During sex or masturbation, I often feel very strong sensations coming from my genital areas",
  MINT_Awareness_SexS_20 = "When I am sexually aroused, I often notice specific sensations in my genital area (e.g., tingling, warmth, wetness, stiffness, pulsations)",
  MINT_Awareness_SexS_21 = "My genital organs are very sensitive to pleasant stimulations",
  MINT_Awareness_SexO_22 = "In general, I am very sensitive to changes in my genital organs",
  MINT_Awareness_SexO_23 = "I can notice even very subtle changes in the state of my genital organs",
  MINT_Awareness_SexO_24 = "I am always very aware of the state of my genital organs, even when I am calm",
  MINT_Awareness_UrSe_25 = "In general, I am very aware of the sensations that are happening when I am urinating",
  MINT_Awareness_UrSe_26 = "In general, I am very aware of the sensations that are happening when I am defecating",
  MINT_Awareness_UrSe_27 = "I often experience a pleasant sensation when relieving myself when urinating or defecating)",
  MINT_Awareness_RelA_28 = "I always know when I am relaxed",
  MINT_Awareness_RelA_29 = "I always feel in my body if I am relaxed",
  MINT_Awareness_RelA_30 = "My body is always in the same specific state when I am relaxed",
  MINT_Awareness_StaS_31 = "Being relaxed is a very different bodily feeling compared to other states (e.g., feeling anxious, sexually aroused or after exercise)",
  MINT_Awareness_StaS_32 = "Being sexually aroused is a very different bodily feeling compared to other states (e.g., feeling anxious, relaxed, or after physical exercise)",
  MINT_Awareness_StaS_33 = "Being anxious is a very different bodily feeling compared to other states (e.g., feeling sexually aroused, relaxed or after exercise)",
  MINT_Awareness_ExAc_34 = "I can always accurately feel when I am about to burp",
  MINT_Awareness_ExAc_35 = "I can always accurately feel when I am about to fart",
  MINT_Awareness_ExAc_36 = "I can always accurately feel when I am about to sneeze",
  MINT_Sensitivity_Card_37 = "In general, I am very sensitive to changes in my heart rate",
  MINT_Sensitivity_Card_38 = "I can notice even very subtle changes in the way my heart beats",
  MINT_Sensitivity_Card_39 = "I often notice changes in my heart rate",
  MINT_Sensitivity_Resp_40 = "I can notice even very subtle changes in my breathing",
  MINT_Sensitivity_Resp_41 = "I am always very aware of how I am breathing, even when I am calm",
  MINT_Sensitivity_Resp_42 = "In general, I am very sensitive to changes in my breathing",
  # MINT_Sensitivity_Sign_43 = "When something important is happening in my life, I can feel immediately feel changes in my heart rate",
  # MINT_Sensitivity_Sign_44 = "When something important is happening in my life, I can immediately feel changes in my breathing",
  # MINT_Sensitivity_Sign_45 = "When something important is happening in my life, I can feel it in my body",
  MINT_Sensitivity_Gast_46 = "I can notice even very subtle changes in what my stomach is doing",
  MINT_Sensitivity_Gast_47 = "In general, I am very sensitive to what my stomach is doing",
  MINT_Sensitivity_Gast_48 = "I am always very aware of what my stomach is doing, even when I am calm",
  MINT_Sensitivity_Derm_49 = "In general, my skin is very sensitive",
  MINT_Sensitivity_Derm_50 = "My skin is susceptible to itchy fabrics and materials",
  MINT_Sensitivity_Derm_51 = "I can notice even very subtle stimulations to my skin (e.g., very light touches)",
  # MINT_Sensitivity_SexC_52 = "When I am sexually aroused, I often feel changes in the way my heart beats (e.g., faster or stronger)",
  # MINT_Sensitivity_SexC_53 = "When I am sexually aroused, I often feel changes in my breathing (e.g., faster, shallower, or less regular)",
  # MINT_Sensitivity_SexC_54 = "When I am sexually aroused, I often feel changes in my temperature (e.g., feeling warm or cold)",
  MINT_AttentionCheck_1 = "I can always accurately answer to the extreme left on this question to show that I am reading it")
```
